\vspace{-.5cm} Lights: a generalized joint model for high-dimensional multivariate longitudinal data and censored durations \vspace{.5cm}

### 2021-05-10 paper.tex
add graphical model

\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{mathrsfs} 
\usepackage{natbib}
\usepackage{setspace}
\usepackage{dsfont}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{subfigure}
\usepackage{algpseudocode}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\newcommand\mycommfont[1]{\footnotesize\ttfamily\textcolor{orange}{#1}}
\SetCommentSty{mycommfont}
\SetKwInput{KwInput}{Input} 
\SetKwInput{KwOutput}{Output}

@@

>>>>

\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{mathrsfs} 
\usepackage{natbib}
\usepackage{setspace}
\usepackage{dsfont}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{subfigure}
\usepackage{bm}
\usepackage{tikz}
\usetikzlibrary{fit,shapes,shadows,arrows,positioning,graphs}
\usepackage{algpseudocode}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\newcommand\mycommfont[1]{\footnotesize\ttfamily\textcolor{orange}{#1}}
\SetCommentSty{mycommfont}
\SetKwInput{KwInput}{Input} 
\SetKwInput{KwOutput}{Output}

@@

\subsection{Graphical model for the lights}
Figure~\ref{fig:graphical-model} below gives the graphical representation for the lights model to get a beter view of the dependence structure for the model.
\begin{figure}[!htb]
\centering
\resizebox{.9\textwidth}{!}{
\begin{tikzpicture}
\hspace{3cm}
\tikzstyle{main}=[circle, minimum size = 18mm, ultra thick, draw =black!80, node distance = 13mm,text centered]
\tikzstyle{var}=[rectangle, minimum size = 16mm, ultra thick, draw =black!80, node distance = 13mm,text centered]
\tikzstyle{connect}=[-latex, thick]
\tikzstyle{box}=[rectangle, draw=black!100]
  \node[var, fill = white!100] (beta) [] {\Large$\bm{\beta_k^l}$};
  \node[var, fill = white!100] (xi) [below=4cm of beta] {\Large$\bm{\xi_k}$};
  \node[var, fill = white!100] (gamma) [below=3cm of xi] {\Large$\bm{\gamma_k}$};
  \node[main, fill = white!100] (G) [right=4cm of xi] {\Large$\bm{G_i}$};
  \node[main, fill = white!100] (mu) [right=4cm of beta] {\Large$\bm{M_{ik}^l(t)}$};
  \node[main, fill = black!30] (Y) [right=of mu] {\Large$\bm{Y_i^l(t)}$};
  \node[main, fill = white!100] (b) [below=0.7cm of Y] {\Large$\bm{b_i^l}$};
  \node[var, fill = white!100] (phi) [above=of Y] {\Large$\bm{\phi_l}$};
  \node[var, fill = white!100] (Sigma) [right=of b] {\Large$\bm{D}$};
  \node[main, fill = white!100] (W) [below=of b] {\Large$\bm{\varphi_i(t)}$};
  \node[main, fill = white!100] (lambda) [right=4cm of gamma] {\Large$\bm{\lambda_i(t)}$};
  \node[main, fill = black!30] (T) [right=of lambda] {\Large$\bm{T_i}$};
  \node[main, fill = black!30] (X) at (3, -8.3) {\Large$\bm{X_i}$};

  \path [->,draw,ultra thick]
        (beta) edge (mu)
        (G) edge (mu)
        (b) edge (mu)
        (mu) edge (Y)
        (Sigma) edge (b)
        (phi) edge (Y)
        (xi) edge (G)
        (X) edge (G)
        (gamma) edge (lambda)
        (W) edge (lambda)
        (G) edge (lambda)
        (X) edge (lambda)
        (lambda) edge (T)
        ;

  \node[rectangle, inner sep=8mm,draw=black!100, ultra thick, fit= (beta) (xi) (gamma),label={[anchor=west, yshift=-0.5cm, xshift=-10mm]{\Large$\bm{k = 1...K}$}}] at (0, -4.6) {};
  \node[rectangle, inner sep=4mm,draw=black!100, ultra thick, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi)] {};
  \node[rectangle, inner sep=4mm, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi),ultra thick] at (12, 3.5) {\Large$\bm{l = 1...L}$};
  \node[rectangle, dashed, inner sep=3mm, draw=red!100, fit= (b) (W),ultra thick] {};

  \node[rectangle,inner sep=6mm, draw=black!100, label=center:\rotatebox{90}{\color{white}\Large{\textbf{Longitudinal}}}, minimum width=1cm, minimum height = 6cm, fill = black!50] at (-2.7,0.5) {};

  \node[rectangle,inner sep=6mm, draw=black!100,  label=center:\rotatebox{90}{\color{white}\Large{\textbf{Time-to-event}}}, minimum width=1cm, minimum height = 6cm, fill = black!50] at (-2.7,-8.2) {};

\end{tikzpicture}}
\caption{Graphical representation of the lights model. Square boxes denote observed data while circles denote unobserved (including random) terms. The red-dashed box indicates that the association features and the random effects are correlated, which, in addition to the link with the latent group membership, gives rise to the joint model.}
\label{fig:graphical-model}
\end{figure}
